---
# SECTION: Bibliography opts
# bibliography: "./refs/refs.bib"
# cite-method: citeproc
# citeproc: true
# csl: "./refs/apa-cv.csl"
# link-citations: true
# link-bibliography: true
# suppress-bibliography: true
---

<!-- NOTE: If on Nix, run ./nix/build_env.R prior to rendering -->

```{r}
#| lst-label: lst-r-libraries
#| lst-cap: "R libraries"

base::library(package = knitr) # NOTE: For document rendering
base::library(package = quarto) # NOTE: For document framework
knitr::write_bib(
  x    = base::.packages(),
  file = "./refs/r_packages.bib"
)
```

```{r}
#| lst-label: lst-knitr-opts
#| lst-cap: "Knitr options"

base::options(knitr.kable.NA = "-")
```

{{< pagebreak >}}

# Assignment Instructions

This research proposal is the definitive take-home assignment for the course and
will require that you use many of the skills you have built through the
semester. This assignment allows me to best assess your mastery of literature
review, scientific writing, and sound research design in a format which will
prepare you well for future courses. Whereas the exams and quizzes will test
your knowledge, this assignment will require a strong command of applying the
concepts you've learned. Please write in a manner that would allow this plan to
be followed by someone actually attempting to conduct this research.

In class, we will have workshops, tutorials, and guided writing time to support
you in this project. It would be very wise to start this paper as early as
possible and work on it steadily through the second half of the semester. Robust
research projects in the "real world" are often planned over the course of weeks
or months! Take your time, meet the preliminary deadlines, and use all the
resources available to you - and you will do well on this assessment.

You may find it helpful to work on this alongside your article critique project.
Whereas that critique will focus on your ability to read and recognize ideas in
research, this project will put more emphasis on your own ability to explain and
rationalize certain design decisions.

The end product should contain these 4 sections:

## Introduction

A thorough literature review establishing context for your planned study. You
should use vetted, peer-reviewed sources that add support to the topic you
choose as a valuable and meaningful area of investigation. Scaffold naturally
from foundation concepts in the research area to the "gap" that you are trying
to fill with the proposal. Effectively, you are making an argument for why this
research is needed and providing the necessary information for a reader to
understand your starting point. You will also need to write a clear hypothesis
that articulates the goal of the study and expected outcome.

## Methods

Layout a complete plan for sampling, measures, procedures, and planned analyses
for your study. Your plan should balance ethics, power, and practicality in such
a way that the study could feasibly be completed with adequate time and
resources. You should also reasonably address each area of validity we have
discussed in class and the impact of design decisions on the strength and
generalizability of claims. Where necessary, consider citing previous work in
the area with similar methodology that buttresses your approach. Give detail on
the scale of measurement, and rationale your use of particular statistical tests
that are appropriate for these tests. (*Do not worry too much about in-depth
statistical procedures, that will be covered further in future course - but it
will help to get familiar sooner*)

## Discussion

A hypothetical discussion of what the implications are for whether results are
significant or not. Make sure to clearly connect your "results" back to the
literature and "gap" you provide in your introduction. Explain what your
findings would mean in the context of existing research, and provide appropriate
and rational discussion of limitations and future directions for research.

## References

An APA 7th Edition-style bibliography that contains the full information for all
citations used in the project. If you use tools such as Citation Machine or
Zotero/EndNote, make sure to double-check that citations are correct, as
sometimes automated tools can cause unexpected issues.

# Timeline of Project Steps and Due Dates

Submission of each step on time is accounted for by points for the project.
Please make sure that you stay on track to earn all of your points and so that
you do not risk having an overwhelming amount of work at the end of the
semester.

## Topic Approval

You must submit a brief summary (3 - 4 sentences) of a topic of your choice for
my approval, and include a rough idea of what type of design you could use. This
study must be psychological in nature, but may be in any domain of psychology.
That being said, I would encourage you to choose a topic that both has adequate
amounts of literature about it AND is personally interesting to you. You also
want to ensure that the topic can be investigated through the methods we have
learned in this course. You may have to do an early literature review to ensure
there are enough papers out there in order to write a proper introduction. I
require that you submit this description for approval by Oct 29. (5 pts)

## First Draft

You will provide an early draft of your proposal, which allows me to assess your
progress and direction, and provide you with feedback. Part of this draft will
need to be an annotated bibliography with a minimum of 10 peer-reviewed sources,
published since 2000. An annotated bibliography looks similar to what a
"References" section looks like in a paper, but with written notes for each
citation explaining how it will be used in the paper. I will expect you to at
least have outlined and/or began writing your introduction at this point.
Properly tracking and integrating sources is one of the most difficult parts
about planning research, so please put good time into reading and evaluating
articles for inclusion in your final project.

It is to your advantage to finish as much of your proposal as you can before
this deadline, as I can give more feedback, and it will set you up better for an
easier final submission. This is due by Nov 12. (15 pts)

## Final Draft

A final submission of the completed project. This will, ideally, be a natural
continuation of your chosen topic and draft from the prior parts. I expect this
to be well-written and edited, in APA 7 style, use adequate amounts of
peer-reviewed citations, and flow well in its logic. This is due by Dec 3. (80
pts)

# Rubric

There is no word or page limit or minimum, but please make sure to include
enough content to do justice to the topic and each section, while still being
clear and concise. If you have concerns about your length, please reach out to
me.

| Points | Component                    |
| ------ | ---------------------------- |
| 5      | Topic Approval               |
| 15     | First Draft                  |
| 10     | Final Draft - Writing Style  |
| 20     | Final Draft - Introduction   |
| 20     | Final Draft - Methods        |
| 20     | Final Draft - Discussion     |
| 10     | Final Draft - References     |

# Tips

## Start Early

While you won't be able to start on this project until you have some knowledge
under your belt, I recommend you at least begin considering options for this
project early in the semester. I myself have been guilty of procrastinating
writing, and I know how much a pain it is to have to make it up quickly. Make
sure you spread your writing out and revisit your work to re-edit and add
content where needed.

## DO NOT USE AI

While this is against my course policy in general (see the syllabus), I can't
emphasize enough that you MUST use your own words and work to perform well. AI
is notorious for making up citations that do not exist and mis-citing
information. In such a case, you would not just be guilty of using a prohibited
tool, you would also be plagiarizing. I want each of you to succeed and grow on
your own merits - and using compensatory strategies will take away from your
learning. If you feel you must use it to aid your writing, please triple-check
your work and citations.

## Read More Articles

This seems intuitive, but really, reading well written scientific articles will
help give you an idea of what the flow of scientific writing sounds like. The
APA 7 Manual also has many helpful suggestions for how to approach writing in
this style. Research oftentimes reads very different from other form of
literature, so it is critical to understand how it tends to read and provide
information.

## Use ALL of Your Resources

Come talk to me. Go to the librarians. Read up on research guides from the
library and college. Have the Writing Center help you edit your early work. You
have many opportunities to craft a stellar piece of work - make sure you use
them readily! There is no shame in asking for help, but you must do so early
when there is still time to correct things.
