---
# SECTION: Bibliography opts
# bibliography: "./refs/refs.bib"
# cite-method: citeproc
# citeproc: true
# csl: "./refs/apa-cv.csl"
# link-citations: true
# link-bibliography: true
# suppress-bibliography: true
---

<!-- NOTE: If on Nix, run ./nix/build_env.R prior to rendering -->

```{r}
#| lst-label: lst-r-libraries
#| lst-cap: "R libraries"

base::library(package = knitr) # NOTE: For document rendering
base::library(package = quarto) # NOTE: For document framework
knitr::write_bib(
  x    = base::.packages(),
  file = "./refs/r_packages.bib"
)
```

```{r}
#| lst-label: lst-knitr-opts
#| lst-cap: "Knitr options"

base::options(knitr.kable.NA = "-")
```

{{< pagebreak >}}

# Assignment Instructions

You are to individually write a comprehensive and sophisticated critique and
review of a scientific, peer-reviewed article of your choosing. This article
should be an original, empirical study (i.e., not literature review or
theoretical) somehow related to the field of psychology, and should use
methodology you are at least somewhat familiar with from content in this course.

You should be mindful to avoid biomedical clinical trial studies (like those
that study prescription drugs) or papers that employ designs that are especially
complex - as you likely won't have the knowledge (yet) to fully engage with this
difficulty. I would also recommend you avoid animal research, as we have not
placed a high emphasis on it this semester. Finally, you will also want to
probably stick to quantitative research, rather than qualitative. I would
encourage you to search for research in an area that is interesting to you,
while also making sure that you can actually understand the writing.

The core component of this project is all about interrogating the validity of
some research claims, through the clues that we have discussed this semester.
Think of our article discussions in class (primarily later in the semester). I
want you to write about what went wrong and right in the study *and* make
reasonable suggestion on how it may have been improved. The critique should be
thorough and cover all relevant parts of the study.

APA citations to other literature are not required for your critique, though you
may find it helpful. Do be mindful that if you make a specific suggestion based
off of another piece of literature you MUST cite it. When you make
recommendations, they should be realistic and practical (i.e., not every study
can be a simple random sampling, double-blind experiment).

If you find you are struggling with writing this, remember GVSU has a fantastic
writing center that can help you out. I am also available to answer questions if
you have any.

This project will consist of 3 parts:

1. A submission of your article of interest and a brief summary of the study,
   with the full-text PDF of the paper. You will be expected to independently
find an article that interests you, using the literature review and searching
techniques we discuss early in the semester. Please read through the entire
article before submitting for approval to make sure you are comfortable with it.
I will review and approve your article, before you begin writing, to ensure it
is appropriate for this project. I will not allow changes to your paper topic
after the deadline. This will be due by Oct 29. (5 pts)

2. A submission of an early draft of your critique. I will expect that you have
   accomplished at least outlining your ideas and general thoughts on the
validity of the paper. I will give you feedback on this draft to make sure you
are on the right track for the final work and submission. This will be due by
Nov 12. (5 pts)

3. A final submission of your complete critique. This should address all
   components of the study and discuss the ramifications of both the good and
bad methodological elements. This will be due by Dec 3. (40 pts)

Please know that I will evaluate you critique based on your knowledge from this
course - I understand that you will not likely understand all the decisions made
by researchers, especially in areas like statistics. Just try your best to
address the things you've learned in this course.

# Guiding Questions

I will provide a [Rubric] that outlines the amount of points for each concept
that you are to address. Given that research methods are very heterogeneous
across different papers, journals, and topics, there are no hard and fast rules
for what must be included. However, I will provide some guiding questions to
help you figure out what to write about. I also want to make sure you address
each section of the paper. Please **DO NOT** just write responding in bullet
points from these questions - I want to see your thoughtfulness and creativity
as you navigate the paper:

## Introduction / Literature Review

- Does the paper cite other appropriate peer reviewed research in support of its
claims?

- Is there ample citation used to support any and all statements made? Does is
seem like some statements are lacking supporting evidence?

- Does the paper logically build well to the topic of the paper and establish
context for the study well?

- Is there a "gap" in the research that this study is well-suited to address?

- Is there a clear research question and hypothesis made?

- Within the hypothesis, what type of claims are the authors making?

## Methods

*In the context of this class, this is likely to be the most important area to
focus on!*

- What measures is the study using? Are these established measures in the field,
or new tools made for this study? Is there any information provided to support
the validity and reliability of the measures? I.e., what is the measurement
reliability and measurement validity of this study?

- Do the authors operationalize their research question well? i.e., are the
methods well-suited to the question asked by the end of introduction, is it
logical? I.e., what is the construct validity of this study?

- Do they explain their sampling procedures and is this sampling representative
of the population? I.e., what is the external validity of this study?

- Do the authors give adequate explanation of any data processes (e.g., missing
data, statistics, alpha for significance) that are used?

## Results

*Note: I know you all are not statisticians, just try your best for this
portion*

- Does the paper appear to report p-values/confidence intervals and effect
sizes, and interpret them correctly (i.e., significant or not; small, medium,
large effect)?

- Does the paper report descriptive statistics on the sample? Does this seem
like a representative sample based on those values?

- Are the statistical tests presented in a logical order and supportive of the
research question and methods used?

- Are the statistics appropriate to the scale of measurement of the data (e.g.,
interval, ratio, ordinal, categorical)?

## Discussion

- Are the final conclusions well-supported by the results and methods used? Is
there strong, or only tentative, evidence for these statements?

- Are any potential limitation of the study described and addressed? Do the
authors provide any suggestions to address these limitations for future studies?
Are there limitations that are not fully addressed or transparently reported by
the researchers?

- Do the authors provide any detail for directions in which future research
could build from this work?

# Rubric

There is no word or page limit or minimum, but please make sure to include
enough content to do justice to the article, while still being clear and
concise. If you have concerns about your length, please reach out to me.

| Points | Component                    |
| ------ | ---------------------------- |
| 5      | Topic Approval               |
| 5      | Critique Draft               |
| 5      | Final Draft - Writing Style  |
| 10     | Final Draft - Introduction   |
| 10     | Final Draft - Methods        |
| 5      | Final Draft - Results        |
| 10     | Final Draft - Discussion     |
