---
# SECTION: Bibliography opts
# bibliography: "./refs/refs.bib"
# cite-method: citeproc
# citeproc: true
# csl: "./refs/apa-cv.csl"
# link-citations: true
# link-bibliography: true
# suppress-bibliography: true
---

<!-- NOTE: If on Nix, run ./nix/build_env.R prior to rendering -->

```{r}
#| lst-label: lst-r-libraries
#| lst-cap: "R libraries"

base::library(package = knitr) # NOTE: For document rendering
base::library(package = quarto) # NOTE: For document framework
knitr::write_bib(
  x    = base::.packages(),
  file = "./refs/r_packages.bib"
)
```

```{r}
#| lst-label: lst-knitr-opts
#| lst-cap: "Knitr options"

base::options(knitr.kable.NA = "-")
```

{{< pagebreak >}}

# Assignment Instructions

"Reading Evidence" for this course, is some record of your note-taking or
engagement with the **assigned textbook readings** for each week. I recognize
that notes can look very different from person to person, and I will respect a
variety of approaches and still award full points. However, it is most critical
to me that you demonstrate a **complete and thorough reading of the chapter**,
meaning I do expect you to at least reference content from each and every
section and subsection in the chapter. Your notes do not have to include
information from sidebars or example questions, e.g., "test your knowledge" -
but you are welcome to include these if you think it will be helpful to you. You
do not have to be overly deep and detailed, and it is okay to admit/show
confusion on a certain topic - but please do give a good effort. I would
encourage you to also connect the text to activities that we do in class and
also share your own thoughts about concepts, rather than just writing things
from the book.

When attempting to get full points, you should ask yourself, "Do these notes
seem like someone who has read the textbook, *not* just attended the lecture?"
If your notes appear to just a replication of content from class slides or
purely based on the lecture (i.e., not reading), your work will receive 0
points. You should not be merely reading the textbook and watching the
lectures, but actively engaging with them by writing and recording information.

These notes can be in a digital (typed) form, or a physical form (handwritten).
If you take notes by hand I will have you submit photos (.jpg or .png) of your
notes, and if you type your notes, please provide them in a .docx or .pdf
format.

I require that you submit reading evidence for any 5 of the 14 chapters from
this class. While I encourage you to take good notes on all the chapters (to
help in quizzes and exam review), I will only grade the 5 you submit. Each
submission will be worth 10 points, for a total of 50 points in this category. I
will grade these leniently so long as you have covered all the content (as I
described above), and provide feedback if there are any ways I think you could
make more use of the notes. You do not *have* to take my advice that I offer on
your submission, I just offer it for your consideration. If your work is below
standard for full-points, I will make that clear to you and inform you of what
changes are needed for full points.

As for due dates, I require that you submit at least 1 of the reading evidences
for 1 of the chapters by Sept 10, so that I can give early feedback to get
everyone started. Then, the remainder of the evidences are due near the end of
the semester, on Nov 26.

# Tips for Better Notes

There are many good ways to take notes on text and lecture material, and I
cannot decide what is most suitable for you. I will provide some initial tips to
help you get started, and, hopefully, give you some ideas. I will also provide
an example of my own notes on a chapter from a different textbook, so you may
use that as a source of inspiration if you choose.

## Keep Consistent Style

Throughout each unit, reading, lecture, and week, I would encourage you to keep
your style of note-taking relatively consistent and organized. This will be
especially helpful during open-notes quizzes and when you are filling out exam
study guides. If you choose to use bolding, underlines, italics, and/or colors,
please do so in an informative and intuitive way.

## Use Structure

I use indented bullet points like this:

- Section 1
  - Subsection 1
  - Subsection 2
    - Notes

to keep topics clearly organized, like you would find in a presentation or
chapter reading. While you do not have to follow that style exactly, do think
about using some structure to keep related concepts grouped together. Along with
the styling options I highlighted above, you have a nice variety of ways to
keep your notes in a readable, accessible manner.

## Think Abstract

It is very easy to just take notes on what is written exactly in the book and
nothing more (in a very concrete manner). It is advantageous to try to connect
concepts to examples and add your own thoughts in. I personally like giving
"commentary" on what I read as I write, so I basically have to take the content
in and react to it somehow. Doing things like this can aid in memorization and
also help connect topics across units. You learn best when you find a way to
make the content *applicable to you*.

## Read BEFORE Lectures

While this is a hard habit to make, it is one likely to pay dividends. I would
strongly suggest that you read the textbook chapter for a week before you come
to the lecture with the corresponding content. It will help familiarize you with
the concepts and prompt you to consider what questions you may have. That way,
in class, you can readily ask me about things that are confusing. I like to take
notes from the book, and then "mark them up" with content from the lecture to
help connect the spoken content with the written material.
