---
# SECTION: Bibliography opts
# bibliography: "./refs/refs.bib"
# cite-method: citeproc
# citeproc: true
# csl: "./refs/apa-cv.csl"
# link-citations: true
# link-bibliography: true
# suppress-bibliography: true
---

<!-- NOTE: If on Nix, run ./nix/build_env.R prior to rendering -->

```{r}
#| lst-label: lst-r-libraries
#| lst-cap: "R libraries"

base::library(package = knitr) # NOTE: For document rendering
base::library(package = quarto) # NOTE: For document framework
knitr::write_bib(
  x    = base::.packages(),
  file = "./refs/r_packages.bib"
)
```

```{r}
#| lst-label: lst-knitr-opts
#| lst-cap: "Knitr options"

base::options(knitr.kable.NA = "-")
```

{{< pagebreak >}}

# Exam 1 Format & Structure {#sec-format}

*From the syllabus:*

- Each exam is 50 multiple-choice questions, 2 points for each question.

- Exams will be taken at the start of the class period, but after the quiz
review for the prior week. They will be paper forms (i.e., not on Blackboard).

- Exams are timed, 113 minutes total (previously was 75 minutes).

- Exams are **not** open-note, open-book, or collaborative. You are **not**
permitted to use any form of assistance to aid you during the tests. Do not
discuss the test with other students, even after it has concluded.

- Any indication of academic dishonesty or "cheating" will be investigated
thoroughly and will result in an automatic 0 on the exam for offenders

- Exams will be ended early if all students are clearly finished and content
with their answers.

- Exams will be graded promptly and reviewed the following week.

- Exams will contain content from the entire unit, from lectures, readings, and
other class activities. This will include content from weeks/chapter 1 though 6.

- Exams will not be purely vocabulary-based, students should have a solid
understanding of applications of concepts, ideas, and theories.

# Using This Study Guide & Other Resources {#sec-using}

This study guide is meant to help get students started with guided questions and
tasks that will aid performance on Exam 1. It is laid out as examples and
open-ended questions to provoke thought on the most pressing questions of each
chapter. You may consider using the slides, recorded lectures, and textbook to
help you address each part. However, there are other valuable resources you may
use to help you prepare:

- Review the textbook and professor learning objectives throughout the slides
and chapters.

- Use the questions ("Check Your Understanding") throughout the chapters to quiz
yourself and use the lengthy review sections at the end of each chapter to get a
nice sampling of practice activities.

- Use the results and answers from the weekly quizzes to identify areas of
need for studying.

- Make flashcards for important vocabulary.

- Re-watch recorded lectures to see if you missed any classes and to ensure you
haven't missed any critical content.

- If you exhaust your other options for reviewing content, please feel free to
ask me questions as well.

If you wish to perform your best, you should use a combination of all of these
available resources to help you prepare. Furthermore, I make no guarantee that
this study guide will contain *all* the information on the exam - it is the
student's responsibility to review all materials related to the first 6 weeks of
content.

# Chapter/Week 1 {#sec-ch-1}

- What is a research **producer**? What is a job title this person is likely to
have? What sorts of activities is this person likely to perform?

- What is a research **consumer**? What is a job title this person is likely to
have? What sorts of activities is this person likely to perform?

- Describe the procedures, findings, and structure of Harlow's monkey study to
investigate cupboard theory vs. contact comfort theory.

- Describe the concept of **Empiricism** and its relationship to the
**Theory-Hypothesis-Data Cycle.** Define and explain each individual part of the
cycle.

- How are Empiricism, the process of **reproducing** scientific studies, and the
**self-correcting** nature of science related?

- What are **Merton's 4 Scientific Norms**? Be able to give definitions of each
and examples of behaviors that support these norms.

- Why don't we use the word "prove" in science, and why do we prefer using the
**weight of evidence** to describe support for a claim? Write out an example
of what an improper claim statement (i.e., one being too certain) may look like,
and then give a "fixed" version of that statement.

- What are the 3 contexts/types of research? Give an example of a study that
would be described as each type.

- Compare and contrast the methods and trust-worthiness of **scientific
journalism** and **scientific articles published in peer-reviewed journals.**
See if you can find an example of both types, or better, find a piece of
journalism and then the original article the journalism was based upon.

- What citation style do we use in this course? What are the core, important
components of a full citation (Like that found in a "References" section)?
Looking at the information of an article, try to type out the correct formatted
citation for it. What are some shortcuts in Google Scholar or scientific
databases to get the citation information?

# Chapter/Week 2 {#sec-ch-2}

- What are the 4 sources of knowledge or information we can draw from? Which of
these is the most sound?

- Why do we consider research to be superior to **authority**? Provide 2 examples of
faults in trusting authority.

- Why do we consider research to be superior to **personal experience**? Provide 2
examples of faults in relying on personal experience.

- Why do we consider research to be superior to **intuition**? Provide 2 examples of
biases in intuition.

- Describe the dangers of **confounds** and having no **comparison groups.**
What issues do these introduce? Describe an example of a confound.

- What does is mean that research is **probabilistic**? How does this affect how
we apply research findings to individual people?

- Describe the 6 biases we discussed in intuition. Write an example of each
bias.

- What is the difference between an **original empirical article,** a
**literature review**, and a **meta-analysis?** Try to find an example of each
of these using the techniques we learned to find research.

- What type of search engine should I use in order to find *peer-reviewed* journal
articles? Give two examples of appropriate tools. Find a scientific article that
is specifically about traumatic brain injury and recovery.

- What are the procedures for fully inspecting a research article before using
it?

- Why are books in science generally less valued as a source, compared to
scientific journal articles? Connect this back to criticisms of authority.

# Chapter/Week 3 {#sec-ch-3}

- Define a **variable** and a **constant**. Give an example of each in a research
setting.

- What are the 3 different **scales of measurement** for variables? Give an
example of a variable of each type.

- What is the difference between a **measured** and **manipulated** variables?
What are some reasons a measure may have to measured, and could not be
manipulated?

- Compare and contrast **construct** and **operational** variables. What are
examples of both of these? For the construct of anxiety, propose a simple
operational measure.

- What are the 3 types of **claims** we can make? Give one example of each type and
a few keywords that signal each type of claim. Which of these claims requires
the "hardest" burden to investigate?

- What statistical and graphical methods do we have for presenting information
about associative claims? How does one interpret each of these?

- What are the three specified criteria that must be met that allow us to
determine causation between two or more things?

- What are the 4 **claim validities** for examining scientific claims? For each
validity, give one example of a detriment and one example of a benefit. Which of
the validities is only really applicable to causal claims?

- Describe some primary issues in the conclusions of Mak et al. (2023; the
article we walked through in class). With each one of the validities, how well
does the article meet them?

# Chapter/Week 4 {#sec-ch-4}

- In the case of Prof. Gino of Harvard Business School, what were the primary
accusations levied against her, and what was her response? What were the
consequences of her actions?

- Be able to explain the general structure and goals of the **Tuskegee Syphilis
Study** and the **Milgram Obedience Studies**.

- Describe the questionable/bad ethics of the Tuskegee Syphilis Study and the
Milgram Obedience Studies. In what way did these studies cause undue harm or
fail the participants? Connect these failing to specific principles or
guidelines in the **APA Code of Ethics**.

- Enumerate the 3 principles of the **Belmont Report** and the 5 principles of
the APA Code of Ethics. Be able to define each of these *in detail.*

- Describe the relationship between **informed consent**, **deception**, and
**debriefing**. In what cases would deception be allowed?

- What are the governing bodies for ensuring ethical research procedures at any
institution? In what ways can they influence and regulate ongoing projects?

- Explain the difference between the two types of **research misconduct** -
which type was Prof. Gino (credibly) accused of?

- The first chapter mentioned **"Pre-registration"** of hypotheses - which of the
APA Code of Ethics does this best relate to?

- Describe a situation where ethics and study validity may be at odds or in
conflict. What is an example of a study that would be scientifically valid, but
not ethical?

# Chapter/Week 5 {#sec-ch-5}

- What type of variable requires a **conceptual definition?**

- What are the 3 types or mediums of psychological measures? Provide an example
of each type and describe what these might look like in practice.

- What is the relationship between measurement **reliability** and **validity**?
What claim validity do these both fall under?

- Describe the concept of reliability: what is a good synonym for it? Provide a
real life example of something "unreliable" in the measurement sense. What are
the 3 types of reliability discussed in class?

- What is the most common graphical and statistical method to assess
reliability? How does one interpret each of these graphs and statistics? (You do
not need to know how to calculate statistics, but you should know what certain
values would imply)

- Define measurement validity - what is a good synonym for it? What are the 5
types of measurement validity we discussed in class? Which of these are the
"weakest" or the most subjective?

- What are the two methods by which to investigate **criterion validity**? What
sorts of analyses do we use in the case of either type?

- Using the visual analogy of targets (as presented in class), what would a
reliable, but invalid tool look like?

- By what methods can we find established measures for common psychological
constructs? How is this similar to searching for scientific literature?

# Chapter/Week 6 {#sec-ch-6}

- When we use the terms **survey** or **pool** what type/medium are we referring
to? What are the roughly 4 types of questions we talked about in class? Write an
example of each question type.

- What are the 4 threats we discussed in how questions are written? What are the
available solutions to address each one of these threats?

- Describe what a **response set** is and why it is undesirable in participant
responses. What are the 3 to 4 response sets we talked about, and how can we
attempt to prevent them in our research?

- Describe the concerns in long-term memory and peoples' ability to introspect
on *why* they do something, which could affect our survey results?

- Describe the difference between an **observational measure** and a
**self-report** one. Why might a psychologist see one as more "objective" than
the other?

- What are the 3 major concerns to measurement validity in observational
measures? Give an example of each one of these occurring and how we might solve
each.

- In what ways may we choose to use deception in observation tools to enhance
validity?

# Inter-chapter Questions {#sec-inter-chapter}

These questions are meant to compound different ideas from the lecture and
synthesize what we have learned so far. They are difficult, but also
realistically how complex research normally is.

- I want to run a study observing people at my local mall and their shopping and
impulsive buying tendencies - what sort of consent do I need from the
participants? If I want to give them a self-report form, and interact with them
directly, does that change how I need to get consent? Is there an existing
measure for understanding shopping tendencies I can find somewhere? If I need to
make a new measure, what sorts of questions do I put on it?

- I want to publish research that I did as (hypothetically) a high-school
student. I didn't have any supervision but I planned and ran it all just fine,
it was a study about giving supplements to people and seeing their reactions
over time. Now I can't get any journal to publish it, only because I am a high
school student and don't have credentials. What scientific principals may be
violated here, both by journals and by the student?
