---
# SECTION: Bibliography opts
bibliography: "./refs/refs.bib"
cite-method: citeproc
citeproc: true
csl: "./refs/apa-cv.csl"
link-citations: true
link-bibliography: true
suppress-bibliography: true
---

<!-- NOTE: If on Nix, run ./nix/build_env.R prior to rendering -->

```{r}
#| lst-label: lst-r-libraries
#| lst-cap: "R libraries"

base::library(package = knitr) # NOTE: For document rendering
base::library(package = quarto) # NOTE: For document framework
knitr::write_bib(
  x    = base::.packages(),
  file = "./refs/r_packages.bib"
)
```

```{r}
#| lst-label: lst-knitr-opts
#| lst-cap: "Knitr options"

base::options(knitr.kable.NA = "-")
```

{{< pagebreak >}}

# Contact Information

**Instructor:** Quinton Quagliano, M.S. (he/him/his), Adjunct Professor of
Psychology

**Office:** AuSable Hall (ASH) 1307 - Shared Adjunct Faculty Office

**Office Hours:** Fridays, 2:00pm - 5:00pm EST

**Phone:** 616-331-2976 (Zoom Phone; Not Recommended)

**Email:** [QuagliaQ@gvsu.edu](mailto:quagliaq@gvsu.edu) (Strongly Recommended)

# Course Overview

## Prerequisites

- [WRT-150](https://www.gvsu.edu/catalog/course/wrt-150.htm)
- [PSY-101](https://www.gvsu.edu/catalog/course/psy-101.htm)
- [STA-215](https://www.gvsu.edu/catalog/course/sta-215.htm) or [STA-312](https://www.gvsu.edu/catalog/course/sta-312.htm)
- From these courses students should have a reasonable familiarity with
fundamental concepts in psychology and statistics prior to this course
- Students should also be prepared to write in a coherent and clear way, and be
able to reasonably integrate evidence into arguments and statements

## Successive Courses

- [PSY-350](https://www.gvsu.edu/catalog/course/psy-350.htm)
- [PSY-400](https://www.gvsu.edu/catalog/course/psy-400.htm)
- These courses will expand on the students' skills established in this course,
in more applied projects and assignments

## Meeting Information

**Modality:** In-person, synchronous, traditional classroom setting

**Location:** AuSable Hall (ASH) 1142 Classroom

**Time:** Tuesdays, 6:00pm - 8:50pm EST

## Textbooks

### Required Text

@morlingResearchMethodsPsychology2021

This text is provided through the GVSU SAVE program, learn more about how it
works here: <https://lakerstore.gvsu.edu/GVSUSAVEStudents>. Note that you may
have to opt out of this program, by Sept. 6th, if you wish to purchase a
physical copy. The link to access this text from Blackboard will be near the top
of the page.

### Recommended Text (Optional)

@americanpsychologicalassociationPublicationManualAmerican2020

I would recommend you purchase a copy of this text, for reference during this
course and future projects. I still regularly use my own during professional
work, and it is a wealth of resources and suggestions for better scientific
writing.

## Course Description

3-credit course.  

This course is focused on developing an understanding of philosophy, logic, and
procedures of good science. We will cover a variety of experimental and
observational methodologies in psychology, and discuss their respective
strengths and weaknesses. Attention will be paid to developing rigorous
procedures in psychological research and assessing/critiquing scientific
literature. We will also explore ethics, bias, and validity in study design.
Scientific writing and critical reading will be essential skills in this course.

## Learning Objectives

At the end of this course students are expected to be able to:

### Course Objectives

- **Comprehension/Describe:** Describe the details of summarize the essence of
research articles
- **Application/Write:** Write clearly and cogently in a scientific way
- **Evaluation/Evaluate:** Evaluate strengths and weaknesses of empirical
studies consistent with the standards of psychological science

### Professor's Objectives

- Evaluate, summarize, and maturely discuss the merits and limitations of
research studies
- Conduct effective literature reviews that are inclusive of all relevant
evidence
- Make testable hypotheses supported by appropriate study design and references
- Write scientific papers clearly in the APA 7th edition style
- Understand the importance of a high-standard of ethics in research

## Course Format

This is an in-person, synchronous course that will meet in a traditional
classroom setting for roughly 3 hours every Tuesday of the Fall semester. Class
periods will consist of a combination of activities that support the engagement,
attention, and learning of students for the entire 3 hours. Planned activities
include: lectures, in-class discussion, demonstrations, [Quizzes], [Exams], etc.
Breaks will be provided intermittently throughout the course periods. Prepare
for class periods to last the entirety of the scheduled course time. In-person
classes will not be recorded, but some materials will be available to students
who may have missed a class period due to excused absences (see [Attendence] and
[Due Dates]).

Outside of class, students should work diligently and efficiently on assigned
coursework. **Textbook readings, as indicated on the [Schedule], are always
required and not optional.** The readings will be tested upon and are essential
for being prepared for content during the class period. I also require you
submit your textbook notes for a subset of the chapters (i.e., "[Reading
Evidence]") In this course, my lectures and the assigned readings will be closely
linked and should be viewed as complimentary to each other. I will ensure
lectures cover the key content from each chapter. We only meet once every week,
so students are expected to manage their own time well, and to finish all
assignments in advance of the deadlines provided in the [Schedule].

# Course Policies

This course is subject to the general GVSU policies listed at
<http://www.gvsu.edu/coursepolicies/>. Please review all content on that webpage
in addition to what is written here. If you have questions or concern about any
of these policies, please contact me.

## Contacting Me

Prior to contacting me, please review this syllabus, relevant assignment sheets,
and presentations and make sure the answer you seek is not already there first.
While I always invite questions and communication, I ask that you are discerning
in using your available resources first.

If you do need to reach out, refer to my [Contact Information]. **Please
prioritize using email, and include your full name, course number, and section
number in the subject line, as well as a description of what you need help
with**. An example would be:

"Re: Riley Quagliano, PSY-300 Section 10, SPSS Help for Assignment 2"

Be thorough in your email and tell me what resources you have already used to
try to address your concerns. Detail is helpful so that I am able to fully
understand and attend to your concern. I am generally able to send responses
within 24 hours during weekdays, but please allow me up to 48 hours to respond.
If I haven't responded within 48 hours (during weekdays), please send me a
remainder email - I promise I am not ignoring you! If you email me during the
weekend or later on a Friday, I cannot guarantee a response any earlier than
Monday.

Of course, you are always welcome to ask to schedule a video chat or office
visit, or just stop by during my listed office hours - I'm happy to receive
visitors for questions about the course or to chat about other things. I usually
hang around campus after the scheduled course time, so you may catch me after
class for shorter conversations.

## Integrity, Plagiarism, & Academic Dishonesty

This course will challenge students to grow skills in responsible and ethical
research, in which one of the most essential abilities is writing in a way that
gives proper attribution and credit. When drafting a paper, presentation,
report, or any type of assignment we **must** take care to use our own words and
thoughts, and cite the scholars that we build from. In the academic world,
plagiarism, fabrication, and confabulation are some of the most egregious
crimes, and have resulted in de-funding of labs, loss of grants, and the
destruction of professional reputations.

I will hold students to the same high standards of the professional research
world, as I wish to ensure all of you are able to leave this course confident in
your ability to conduct and write ethical research. I will help all students
steadily build these skills, and do expect early mistakes that need correction.
However, any evidence of intentional or negligent plagiarism or academic
dishonesty will be handled in line with the GVSU Student Code.

As described by the GVSU Student Code, “Offering the work of someone else as
one's own is plagiarism...” “Any ideas or material taken from another source for
either written or oral presentation must be fully acknowledged.” “Depending on
the instructor's judgment of the particular case, he/she may ... give a failing
grade for the ... entire course.” Simply rearranging the words or substituting
synonyms in the original source is still plagiarism. Details about the APA
method for citing research will be provided during the course. Furthermore,
students should not self-plagiarize, that is, reuse their own work from another
course.

Students are permitted to be in study groups and learn from one another, but all
submitted work should be distinct and unique to each individual. I would
recommend you only study in groups for quizzes or exams, but complete other work
(e.g., Article Critique, Research Proposal, etc.) as an individual, to avoid
unintentional plagiarism. Students in other sections of this course, with other
professors, may not have perfectly aligned content with the pace of this
section.

## Use of AI Tools

The following statement should be understood as constituting my policy on use of
AI tools in this course:

AI Policy Statement by David A. Joyner
([davidjoyner@fediscience.org](mailto:davidjoyner@fediscience.org))

> "We treat AI-based assistance, such as ChatGPT and Copilot, the same way we treat
> collaboration with other people: you are welcome to talk about your ideas and
> work with other people, both inside and outside the class, as well as with
> AI-based assistants.
>
> However, all work you submit must be your own. You should never include in your
> assignment anything that was not written directly by you without proper citation
> (including quotation marks and in-line citation for direct quotes).
>
> Including anything you did not write in your assignment without proper citation
> will be treated as an academic misconduct case. If you are unsure where the line
> is between collaborating with AI and copying from AI, we recommend the
> following:
>
> 1. Never hit "Copy" within your conversation with an AI assistant. You can copy
> your own work into your conversation, but do not copy anything from the
> conversation back into your assignment.  Instead, use your interaction with the
> AI assistant as a learning experience, then let your assignment reflect your
> improved understanding.
>
> 2. Do not have your assignment and the AI agent open at the same time. Similar
> to above, use your conversation with the AI as a learning experience, then
> close the interaction down, open your assignment, and let your assignment
> reflect your revised knowledge. This includes avoiding using AI directly
> integrated into your composition environment: just as you should not let a
> classmate write content directly into your submission, so also avoid using tools
> that directly add content to your submission."

While "AI", as we know it, may be a useful tool for learning and
troubleshooting, it is never an acceptable replacement for graded and
professional work. For the work in this course, I'd strongly recommend you rely
upon class content, the textbook, and peer-reviewed scientific research to study
and build your skills. If I have reason to believe that AI tools have been used
to generate work passed off as your own, I will investigate it the same as any
other form of academic dishonesty (see [Integrity, Plagiarism, & Academic
Dishonesty]). I implore you to maintain a high level of integrity in your work
and I will take appropriate measures to detect and investigate unethical use of
AI tools.

## Respectful and Inclusive Environment

All students, in all their virtual and physical interactions with myself and one
another, are expected to treat each other in a mindful and professional manner.
Please be respectful of your classmates' diverse identities, backgrounds, and
beliefs. Even in disagreements or tense discussion, students should remain
constructive in their arguments, and not personally attack one another. If at
any point you feel that another student has acted maliciously, aggressively, or
disrespectful towards you, please notify me immediately, so I may address it.
Additionally, if you have concern about my own conduct, please do let me know
so, I can correct it. Those that continue to act in a way that is harmful to the
classroom environment may be dismissed from the course and referred to college
administration for further discipline.

## Electronic Devices

Students are permitted to use computers or other devices to take notes and
complete assignments during the class period. In fact, I encourage you to bring
internet-capable devices to our class meetings, as they will likely be helpful
in certain in-class activities and quizzes. However, refrain from doing any
activities during class that distract those around you (e.g., watching videos,
playing video games, listening to music, distracting loud keyboards, etc.) If I
suspect that you are harming the learning experience of other students, I will
ask you to either cease the behavior or switch to pen-and-paper for note-taking.
Please ensure all electronic devices are silenced during class (medical devices
that must alert for the well-being of the user are exempt). Regardless of
whether you intend on using an electronic device for class, I'd recommend having
a pen/pencil and paper, in case a device crashes or is out of battery.

## Food and Drink

It is fine to eat and drink during the class period (except for during exams and
quizzes), as long as you are able to do so quietly and without interrupting
others. Please do not make a mess, as to be respectful to those who diligently
clean our rooms.

## Course Materials and Recordings

For any materials created by me, such as notes, slides, handouts, assignments,
etc. - do not share these materials with students who are not in the section,
now or in the future. You may keep them for your own personal reference. I
cannot allow students to keep copies of exams or quizzes, even after they are
graded. Resources that I provide that are already public or semi-public, like
articles and webpages, are fine to share with anyone.

Class periods will not be recorded by me, nor are students permitted to record
the class lecture with any form of video, audio, or transcription equipment. I
will provide a separate recording of the lecture(s), as well as accompanying
slides, for any given class meeting *after* the class meeting it compliments.
These materials are provided to help students review the lecture content, if you
believe there is something you may have missed during the class period. **The
posted lecture recording and slides are NOT a substitute for being in class at
the designated meeting time - as you will miss important in-class discussions
and activities, if you are not present.**

## Attendance

Please try to make it to class, on time, for all scheduled class periods. Coming
in late may disrupt your peers' learning and my ability to lecture. It is
difficult to keep up with the course content if you miss part of or all of the
class. While I understand that life circumstances may force you to miss class or
be late on occasion, it will likely impair your ability to succeed in this
course. If you suspect attendance will be consistently difficult for you in this
course, I would suggest that you consider leaving this section. If you expect to
miss a class period, or do so due to an emergency, please reach out to me to
make up work (see more details in [Due Dates]).

## Due Dates

**All due dates, as they are listed in the schedule, are firm.** You should
closely track your own progress in the course and ensure that you are keeping on
pace. You should plan to make every attempt to attend our regularly scheduled
course times so that you may complete any necessary assessments. Take-home
assignments are due at the start of class time.

If you expect that a qualifying pre-existing obligation, that cannot be moved,
will interfere with class time, please reach out to me **at least one week prior
to the affected course meeting.** So that we may make arrangements for you to
turn in relevant work, and take any missed [Quizzes] or [Exams]. If you find
yourself in an emergency situation that prevents your attendance in
class/turning in work on time, please notify me as soon as possible and provide
documentation on what your emergency was (e.g., doctor's note).

I will work with students to ensure you have the opportunity to submit your work
and make it up. **Barring extraordinary circumstances, you must reach out to me
within 48 hours of the original due date to coordinate an appropriate time to
submit the work.**

In the cases of missed work needing to be made up, I ask that we complete the
work prior to the next class period as to not delay review of exams or quizzes
for your peers. **It is the student's responsibility to contact me regarding
make-up work - failure to do so in a timely manner (48 hrs) will result in the
total forfeiture of points.**

Barring exemptions, as explained above, late work will have 25% of earned points
deducted per each day late (including weekends). Work is considered to be a day
late immediately after submission for assignments at the start of the class
period. Example: a paper (50 points total) is submitted 2 days late, and earns
40/50 points - this paper will have 50% of earned points deducted, resulting in
a 20/50. Thus, after 4 days late, an assignment will not be eligible for any
points.

Please submit all assignments through their respective [Blackboard Ultra]
submissions, regardless of whether they are late or not. Do not email me or hand
in paper copies of assignments unless I request so - I will redirect you to
submit through Blackboard.

## Changes to the Syllabus and Schedule

It is plausible that events during the semester may require that I modify the
syllabus or schedule. As soon as I know such a change must be made, I will
notify you all through Blackboard and those messages should be understood as
amending this document.

# Blackboard Ultra

I will be making liberal use of Blackboard Ultra to communicate, administer
assignments, and share course materials. Please make sure you have a working
knowledge of this platform and can reasonably navigate it to find messages and
submit assignments. You should have access to an e-learning Blackboard tutorial
course that can show you the basic functions. I will try to use Blackboard to
keep you all engaged during the weeks and provide additional resources to those
who are interested. Prior to the course starting, please browse around and make
sure you can access and view everything alright. I will attempt to keep
information between this syllabus and schedule, and Blackboard as congruent as
possible. If you experience technical problems with Blackboard or are not able
to get things working in your browser, contact the help desk:

**Website:** <https://www.gvsu.edu/elearn/help/blackboard-student-help-2.htm>

**Email:** [helpdesk@gvsu.edu](mailto:helpdesk@gvsu.edu)

**Phone:** (616) 331-3513

If you find issues in due dates, grades, assignment format, etc., that appear to
be a mistake by me, please contact me and let me know, so I can promptly fix it.

# Grading

Summative assessment (i.e., graded assignments) are key to evaluating a
student's success in learning the content of this course. I have set up this
course to be forgiving for the sake of learning, as mistakes and missteps are
often part of the growth process. However, I must fairly evaluate the abilities
each student builds in this course, and must ensure that the learning objectives
are met. That being said, I care deeply about the effort and motivation that you
have put into this course and have included assignments that award points for
good-faith attempts and offer room for improvement. My goal is to readily submit
grades on [Blackboard Ultra] as I complete them, so that you may be
well-informed to your current status. All grade functions on Blackboard should
be fully set-up so that you can easily track your progress and success.

**I cannot and will not "bump", "curve", "round", or "scale" grades at the
individual student level, due to any circumstance. Please do not ask me to do
this.** Such a change in student's grades can lead to unfairness and
subjectivity in how students are assessed, and would be unfair to your peers. In
the case of an error in grading or poor class performance on a test question, I
will consider the need to drop questions or adjust grading for all students
equally. The standard for what constitutes certain letter grades (e.g., A, A-,
B, etc.) in this course will be presented in this syllabus, and is subject to
(downward) change if I feel it is necessary.

I will provide an accurate breakdown of the sources of points, and students are
expected to monitor their own success throughout the term. If your performance
is below what you would like at any point, please talk to me (see [Contacting
Me]) or make use of the [Additional Resources]. Please make early adjustments to
avoid any last minute issues that prevent you from obtaining the success you'd
like.

It is to the advantage of you, the student, that many points are possible in
this course. That way, a few poor performances can be made up by consistent
effort on the other available opportunities. The point ranges are approximations
of the percents - please note your final letter grade will be determined solely
by the percent range it falls in. If I remove quiz or exam questions or change
the point total at any point, the point ranges will no longer properly apply.

| Letter Grade  | Percent     | Points        |
|-------------- |------------ |-------------- |
| A             | >93         | >474.3        |
| A-            | 90 - 92.99  | 459 - 474.2   |
| B+            | 87 - 89.99  | 443.7 - 458.9 |
| B             | 83 - 86.99  | 423.3 - 443.6 |
| B-            | 80 - 82.99  | 408 - 423.2   |
| C+            | 77 - 79.99  | 392.7 - 407.9 |
| C             | 73 - 76.99  | 372.3 - 392.6 |
| C-            | 70 - 72.99  | 357 - 372.2   |
| D+            | 67 - 69.99  | 341.7 - 356.9 |
| D             | 63 - 66.99  | 321.3 - 341.6 |
| F             | <62.99      | <321.3        |

| Assignment              | Points        | Percentage    |
|-------------------------|---------------|---------------|
| Introductions           | 10            | 2%            |
| Reading Evidence (5)    | 10 x 5 = 50   | 9%            |
| Exams (2)               | 100 x 2 = 200 | 40%           |
| Quizzes (12; 2 dropped) | 10 x 10 = 100 | 20%           |
| Research Proposal       | 100           | 20%           |
| Article Critique        | 50            | 9%            |
| Extra Credit (?)        | -             | -             |
|------------------------ |---------------|---------------|
| Total                   | 510           | 100%          |

# Activity Types

I use a variety of activities as a source of points for your grade in this
course. This way, I can assess your skill in many domains and mediums and can
help you build a well-rounded skill set.

## Introductions

At the start of the semester, I ask that you all contribute to a Blackboard
discussion board, so your classmates and I may learn a little bit about all of
you. Please tell us:

- Your name (with phonemic spelling if you think it would help with
pronunciation) and pronouns (optional - only if you feel comfortable)
- Your year in school (e.g., First-year, sophomore, etc.)
- Your majors and minors
- Briefly identify one area of research in psychology you find interesting - it
can be mundane or complex, broad or specific, just throw something out there.
- Explain one or two interesting facts or hobbies of yours - share anything
you'd like!

## Reading Evidence

For any 5 chapter readings (out of 14) in the textbook, please submit your notes
that you take during your reading of the chapter. Your notes can be handwritten
or typed, and can be in whatever format and style best suits your needs as a
student. I just ask that you are comprehensive and thorough to the content of
the chapter and cover all the sections to some degree. I may make suggestions on
areas for improvement, but will generally award full points if you make a good
faith attempt to cover all the content. It is recommended to do at least some of
these during early chapters, so I may suggest strategies that I think will serve
you well for the remainder of the semester. I do this so that you may be set up
for success in note-taking to best serve you in this course, while also
rewarding your dialogue with the reading.

Of course, I **strongly** recommend that you take good notes for all chapters,
not just the 5 ones you submit. They may aid you greatly in the open-note
quizzes and preparation on the exams.

## Exams

There will be 2 exams in this course. These exams are intended to be cumulative
and will cover content from all prior units and [Quizzes]. Much of the knowledge
in this course is naturally cumulative, so it benefits you to review content
from the previous units. However, the majority of test content will come from
the most recent unit, with fewer questions being dedicated to the prior unit.
The format is as follows:

- Each exam is 50 multiple-choice questions, 2 points for each question
- Exams will be taken at the start of the class period, but after the quiz
review for the prior week. They will be taken on paper scantron sheets.
- Exams will contain content from the entire unit, between lectures AND readings
- Exams are timed, 113 minutes only (previously was 75 minutes)
- Exams are not open-note, open-book, or collaborative. You are not permitted to
use any form of assistance to aid you during the tests. Do not discuss the tests
with other students after it has concluded
- Quizzes and exam will be ended early if all students are clearly finished and
content with their answers
- Exams will be graded promptly and reviewed the following week

## Quizzes

We will be taking quizzes routinely throughout the semester to help cement the
concepts between each class period. For each student, I will drop each student's
lowest 2 quiz grades from your final grade. The format is as follows:

- Each quiz is 10 multiple-choice questions, 1 point for each question
- Quizzes will be taken at the start of the class period on the Blackboard LMS
- Quizzes will be on content covered in the previous lecture and the associated
reading for that lecture
- Quizzes are timed, 23 minutes only (previously was 15 minutes)
- Quizzes are open-note and open-book, that is, you are allowed to use those
resources during the quizzes. Thus, they reward good structure in thoughtfulness
in your notes and preparation (see [Stay Organized])
- You may not collaborate with others during the quizzes, or discuss questions
with other students after the quiz. You cannot use AI tools or the internet to
help you.
- Quizzes and exam will be ended early if all students are clearly finished and
content with their answers
- Quizzes will be graded promptly and reviewed the following week

Because of the fast nature of quizzes, you will not have time to look up answers
to each of questions - please prepare by studying, reviewing, and understanding
the content, using your organized notes and book as a quick backup.

## Research Proposal

This will be one of the most critical and important assignments in the course.
You will be asked to generate an original research proposal that is ethical,
well-designed, and rooted in a mature understanding of the scientific
literature. This project will use many of the skills that you build throughout
this course and should reflect a strong understanding of your capabilities as a
budding researcher. We will discuss this project more after the first few weeks
and I will provide a rubric highlighting my grading standards for this project.

I will require that you identify a general topic for this proposal by Oct 29,
and that you submit a draft of this proposal by Nov 12.

## Article Critique

You will be tasked with independently finding a piece of empirical,
peer-reviewed research in psychology that is interesting and accessible to you.
Then I will ask that you critically assess the entire research piece to the best
of your ability, critiquing the ethics, validity, design, and conclusions of the
study. The full assignment will be discussed more in-depth later in the
semester, as it is most appropriate to begin this project after you have
demonstrated skills in literature review. However, you may want to begin
casually searching for an interesting article early on, as I will ask you get
your choice approved by me. I will provide a rubric highlighting my grading
standards for this project.

I will require that you are able to locate and provide me with the APA-style
citation and full-text PDF of your chosen article. Your choice of article will
need to be conveyed to me by Oct 29, and a draft will need to be submitted by
Nov 12. Before starting this, you will want to be more familiar with many of the
concepts present in the lectures. Later in the semester, we will do in-class
article discussions to help prepare you for writing this critique.

## Extra Credit (?)

At this time, I do not plan on offering any extra credit for this course.
**Please do not ask me to offer it and do not plan on it being offered.** *If* I
find an opportunity that I feel will enhance your experience in this course and
be eligible for extra credit, I will notify you all through Blackboard. *If* I
do add extra credit assignments, they will supplement the existing points total,
rather than adding to the total itself. This means that they will functionally
"make up" for lost points on the other assignments.

# Schedule

This schedule will be a rough plan for the semester. In addition to each
scheduled quiz/exam and in-class activity, keep in mind I will lecture on the
assigned reading for that week. There is the possibility that this schedule will
need to change if lectures take longer than expected or if classes are canceled
unexpectedly. I will communicate if deadlines change.

| Class Date  | Reading   | Quiz / Exam     | In-class Activity     | Due                    |
|------------ |---------- |---------------- |---------------------- |----------------------- |
| Aug 27      | Ch 1      | -               | APA Style Practice    | -                                      |
| Sep 3       | Ch 2      | Quiz 1          | Lit Search Demo 1     | Introductions                          |
| Sep 10      | Ch 3      | Quiz 2          | Lit Search Demo 2     | Reading Evidence I                     |
| Sep 17      | Ch 4      | Quiz 3          | Ethics Case Study     | -                                      |
| Sep 24      | Ch 5      | Quiz 4          | Measures Search       | -                                      |
| Oct 1       | Ch 6      | Quiz 5          | Exam 1 Study Guide    | -                                      |
| Oct 8       | Ch 7      | Exam 1          | Writing Prep          | -                                      |
| Oct 15      | Ch 8      | Quiz 7          | Article Discussion    | -                                      |
| Oct 22      | -         | -               | -                     | -                                      |
| Oct 29      | Ch 9      | Quiz 8          | Writing Time          | Writing Topics                         |
| Nov 5       | Ch 10     | Quiz 9          | Article Discussion    | -                                      |
| Nov 12      | Ch 11     | Quiz 10         | Writing Time          | Writing Drafts                         |
| Nov 19      | Ch 12     | Quiz 11         | TBD                   | -                                      |
| Nov 26      | Ch 13     | Quiz 12         | TBD                   | Reading Evidence II-V                  |
| Dec 3       | Ch 14     | Quiz 13         | Exam 2 Study Guide    | Writing Finals                         |
| Dec 7 - 14  | -         | Exam 2 / Final  | -                     | -                                      |

**Notes on Reading the Schedule:**

- Quiz content always corresponds to the reading and lecture from the *prior*
class meeting, e.g., Quiz 7 will cover content from Ch 7 reading and lecture
content from Oct 8. The week after a quiz, we will review problematic concepts
from that quiz.

- "Writing" is shorthand that represents the article critique AND research
proposal projects

- Chapters 6 (Oct 1) and 14 (Dec 3) and their corresponding lectures, do not
have a quiz associated with them, but will be covered by the exams.

- Chapter 7 and it's associated lecture (on Oct 8) will NOT be covered by exam 1

- The timing of the course final (exam 2) will be decided by the school policy.
I will communicate what the exact date and time of the exam will be later on.

**Other Important Dates:**
<https://www.gvsu.edu/registrar/academiccalendar.htm#5CEEFECB-98D7-18B7-8BE44596135F45D8>

# Additional Resources

Outside myself, the textbook, and course content, there is a wealth of student
resources available to you all. While I will always aim to be helpful and
available to the best of my ability, I strongly encourage you to utilize these
resources to support your learning and accommodation. Unfortunately, I am unable
to offer extensive, individualized help to each student and may refer you to one
of these services should you request that. Please visit the respective webpages
for these services to learn more about what they can offer to you. There are
many more than I can list, and you should definitely look at all the available
services here: <https://www.gvsu.edu/clas/supporting-students-1136.htm>

## Disability Accommodations

**Webpage:** <http://www.gvsu.edu/dss>

Any student who requires accommodation because of a physical or learning
disability must contact Disability Support Services (DSS;
<http://www.gvsu.edu/dss>) at 616-331-2490 as soon as possible. It is the
student’s responsibility to request assistance from DSS. After you have
documented your disability, please contact me to set up an appointment or see me
during office hours to discuss your specific needs in accordance with your
documentation.

Accommodations are always designed to maintain the academic integrity of the
course; student with disabilities are held to the same academic standards as all
other students. Accordingly, if no additional costs (including staff time) are
involved, the instructor will extend such accommodation to anyone who requests
them, whether or not the student has a declared disability. If a requested
accommodation requires special equipment, space, personnel, staff time, or other
resources beyond those normally available to the class, the accommodation will
be offered only if the student has gone through the process that begins by
declaring the disability with Disability Support Services. If you have a
disability and think you might need assistance evacuating the classroom and/or
building in an emergency situation, please make sure I am aware, so I can
develop a plan to assist you.

Please know that I am committed to making my classroom friendly and accessible
to students of all needs and backgrounds. If there is something minor I can do
to my presentations and materials to make them more accessible to you, please do
let me know.

## The Tutoring and Reading Center (One-on-one Tutoring)

**Webpage:** <https://www.gvsu.edu/tutoring/>

**Description**

Tutoring in the College of Liberal Arts and Sciences (CLAS) serves students at
Grand Valley State University by providing tutoring and supplemental
instruction. We foster academic success by providing multidisciplinary content
support and promoting positive study behaviors to cultivate empowered,
persistent learners in an inclusive, accessible, and learner-centered
environment.  

## Fred Meijer Center for Writing and Michigan Authors (Writing Help)

**Webpage:** <https://www.gvsu.edu/wc>

**Description**

The Fred Meijer Center for Writing provides writing assistance to all GVSU
students, on any type of project and at any stage of the process. The Writing
Center employs both undergraduate and graduate writing consultants from across
majors and disciplines. Consultants are trained to help writers brainstorm,
organize, or develop their ideas; and they can help writers edit their own work
and document sources correctly. The Center's services are free and students can
work with an idea, assignment prompt, or draft of their paper. Students can
virtually drop in or schedule an appointment; both appointments and drop-ins are
available during all service hours: (Mon-Thurs 9am-11pm, Friday 9am-3pm, Sunday
2pm-11pm). Due to COVID-19, all writing center services are available online.
Limited in-person consulting may be available; please check the Writing Center’s
website for up-to-date information. All service options (drop- ins,
appointments, email support) can be accessed via the Writing Center’s online
scheduling system - Book It. We look forward to working with you!

## GVSU Knowledge Market (Research, Writing, and Presentations Help)

**Webpage:** <https://www.gvsu.edu/library/km/>

**Description**

The Knowledge Market is an interdisciplinary peer-to-peer collaborative service
that brings together similarly-aligned academic programs to help students
develop their intellectual skills, habits, and identities. The Knowledge Market
offers one-stop support for library research, writing, oral presentations, and
digital projects! Available to help with projects from any class, our
highly-trained consultants are here for you.

We have two convenient locations and offer online sessions, so you can meet with
us from wherever you are. To have a consultation, schedule an appointment or
join the drop-in queue at any of our locations. We look forward to working with
you!

## Psych Friends Peer Mentoring (Peer-to-peer Mentoring)

**Webpage:** <https://www.gvsu.edu/psychology/psych-friends-477.htm>

Psych Friends mentors are upper-level psychology and behavioral neuroscience
students who are trained to provide support in many areas, such as: effective
studying and time management techniques, exam preparation and reflection skills,
understanding the PSY and BNS major requirements, potential jobs and careers in
the field, the process of applying for graduate school, and how to maintain
physical and mental health as a student.  Visit <https://www.gvsu.edu/navigate>
to schedule an online or in-person meeting today!

Psych Friends Peer Mentoring aims to increase the academic success & well-being
of psychology students by connecting upper division psychology majors (mentors)
with students newer to the major (mentees). Psych Friends is a great way to
expand your knowledge on all that the field of psychology has to offer and to
build a social network with others within the psychology community.

Make an appointment with a peer mentor to learn about the psychology and
behavioral neuroscience major requirements, careers, and education paths in
psychology, the graduate school application process, strategies to increase
academic success, and/ or student self-care techniques. Our mentors would love
to get to know you. We have plenty of time slots available to best fit your
needs. Appointments can be made through Navigate and students can choose between
having an appointment in person on campus, or to meet online via Zoom.

## COVID-19 Resources

**Webpage:** <https://www.gvsu.edu/lakerstogether/>

Unfortunately, COVID-19 remains a threat to our student community. Please review
the above link for resources to help protect yourself and others.

# FAQ

**How do you say the professor's name and how should I address you?**

The phonemic spelling is Kwin-tin Kwahg-lee-ah-no. You are welcome to call me
Quinton, Prof. Quagliano, or Prof. Q. Please do not address me as Mr. Quagliano
(I find it odd) or Dr. Quagliano (I have not earned that honorific).

**What is the professor's background?**

I have an B.S. in Psychology (neuroscience concentration) from [Calvin
University](https://calvin.edu/), and an M.S. in Quantitative Psychology from
[Ball State University](https://www.bsu.edu/). I am a full-time
[psychometrist](https://www.napnet.org/what) at Trinity Health Grand Rapids in
addition to my adjunct role here. Generally, I describe myself as being
research-oriented with emphasis on advanced quantitative (statistical) methods.
I have had the pleasure on working on projects in a variety of theoretical
domains, such as education, neuropsychology, neurology, psychiatry, and
audiology. I remain loosely associated with Pine Rest Christian Mental Health
Services, Ball State University, and Trinity Health Grand Rapids
Neurology/Neuropsychology for ongoing research projects.

I was a TA and tutor for students throughout my undergraduate and graduate
education, and have been involved in clinical work (inpatient psychiatry and
outpatient neuropsychology) for the last 6 years. My CV will be posted in the
course Blackboard if you'd like to know more about me.

**Can I talk to the professor about things other than class?**

Of course! I love talking about research, careers, your academic journey, and
your personal goals. You can always email me or stop by during office hours for
a chat. Unfortunately, I cannot offer any research, teaching assistant (TA), or
extracurricular opportunities to students at this time, but I can give you
pointers on where to look for these things if you are interested! I can serve as
a reference or "letter-writer" for your future endeavors, but only if you ask
me.

**Why so many quizzes?**

More assessments mean that a few bad scores won't sink your chances of a higher
letter grade. Constant testing and revisiting of past topics are also excellent
ways to learn and solidify concepts. It also lets me know if the class is
struggling with certain topics, so I have time to re-hash ideas before the
more-important exams. I know it may be stressful to have these every meeting,
but I do promise they have a purpose to them. Take good notes revisit topics
often and you should be okay.

**How can I learn to write better?**

One of the best ways to learn how to scholarly write is to constantly read
published, scientific articles. I've refined my own writing style a lot by just
emulating the style of more experienced scientists. Of course, good writing is a
skill build up over the course of many years; so be patient and consistent in
developing your abilities. I am here to help you prepare your written
assignments, but make sure to use the writing center and other resources as
well!

**Should I drop the course?**

I cannot make that decision for you, but I do encourage you to be constantly
reflecting upon your success in the course. I try to provide timely feedback and
review, so you know how you are performing on things. Sometimes, it is better to
drop a course and return when you are more experienced, and there is no shame in
doing so. I would suggest you speak with your academic adviser prior to making
this decision, so that they can explain any ramifications on your overall degree
progress.

**Can I re-take or re-submit an assignment, exam, or quiz for a revised score?**

No. I give you adequate time, resources, and in-class support to study for
quizzes/exams and prepare assignments. I will give constant feedback so that you
are better equipped for future assignments, but cannot re-grade revised
assignments. I'd like for students to be proactive in creating high-quality work
the first time by starting work early and using good study habits.

**Why are the article critique and research proposal due before the final exam?**

My hope is that, by requiring these due prior to the final exams, you can better
focus your efforts at the end of the semester towards studying and preparing for
the exam in this course, and your other courses. It also means I can grade these
quickly and have your course grade fully updated going into the final. This way,
you know where you are at and can get a sense of your ability to aim for a
certain letter grade. Because I have due dates for your topics and early drafts
of both of these projects, you likely will already have a good start on both
ahead of the due dates.

# Tips for Success

## Back Up Your Work

We have all been in the undesirable position of losing hours of work due to a
sudden power outage or accident. I **strongly** recommend that you use platforms
and methods to maintain your work in case of an accident. Use services like
Microsoft OneDrive/365 or Google Drive to save your work in the cloud, or use
software like git to version control your work. Save regularly and often,
enabling auto-save if it is a feature in the software you use. While I empathize
with the pain of suddenly losing work, technology issues are not an acceptable
excuse for late work - as there are a variety of ways to preemptively protect
your progress.

## Stay Organized

The start of the semester is the best time to establish the right organization
method that keeps you on track. Losing assignments, papers, and notes to the
void can feel like a huge setback. Think critically now about how you want to
organize your physical/digital documents, and get it ready now. Stick with it,
and you'll find it much easier to look back later when you need that knowledge!
But remember to [Back Up Your Work]!

## Create a Weekly Schedule

While I provide a course [Schedule] to give structure to the overall class, I
would recommend setting up a personal schedule for studying and attending to
assignments throughout each week. Procrastinating and trying to rapidly complete
work before deadlines will hurt the quality of your work and that will likely be
reflected in your grade. Establishing good time-management habits early on in
the semester will help you maintain a good balance between your life and
classes.

## Communicate Well With Me

I ask that you regularly attend to your email and Blackboard so that you see
important notifications from me regarding this course. If you need help or have
question please do reach out to me as soon as possible (preferably via email).
Ignorance or avoidance of emails and notification is not an excuse for late or
poor work. I am always happy to point you in the right direction or clarify
something, but I can only do so if you tell me your concerns.

## Take Care of Yourself

Balancing undergraduate studies with the stresses of life is difficult and is a
time of change for many students. Make sure you get enough sleep, eat food and
drink water, and spend time with friends and family. You'll do best in my course
(and every course) when you are at your best mentally and emotionally! I look
forward to supporting you all best I can this term!

*This course is subject to the GVSU policies listed at
<http://www.gvsu.edu/coursepolicies/>*
